Tourism Data Analysis

### 2020-01-21 Application-R/Application-TourismData/Final-results/TourismData-Final-resultsR1.Rmd
Calculating Nemenyi tests

library(tidyverse)
library(Matrix)
library(hts)
library(readr)
library(tibble)
library(kableExtra)
# library(reshape2)
```

<!-- # Box and whisker plots for orthogonal and oblique projections from better models -->

<!-- ```{r, echo=FALSE} -->
<!-- OvernightTrips_OriginalScale_Fc <- read.csv("OvernightTrips_OriginalScale_Fc.csv")[,-1] -->

<!-- OvernightTrips_OriginalScale_Fc %>% -->
<!--   mutate(SquaredE = (Overnight_Trips - Overnight_Trips_Fc)^2, -->
<!--          Fc_horizon = recode(Fc_horizon, "1" = "h=1", "2" = "h=2", -->
<!--                              "3" = "h=3", "4" = "h=4", "5" = "h=5", "6" = "h=6")) %>% -->
<!--   group_by(`R.method`, Fc_horizon, Replication) %>% -->
<!--   summarise(MSE = mean(SquaredE)) -> OvernightTrips_OriginalScale_MSE -->

<!-- OvernightTrips_OriginalScale_MSE %>% -->
<!--   filter(`R.method`%in% c("Base", "OLS", "MinT(Shrink)", "WLS")) %>% -->
<!--   spread(key = `R.method`, value = MSE) %>% -->
<!--   mutate("Base-OLS" = Base - OLS, -->
<!--          "Base-MinT" = Base - `MinT(Shrink)`, -->
<!--          "Base-WLS" = Base - WLS) %>% -->
<!--   dplyr::select(Fc_horizon, Replication, `Base-OLS`, `Base-MinT`, `Base-WLS`) %>% -->
<!--   rename("OLS" = "Base-OLS", "MinT" = "Base-MinT", "WLS" = "Base-WLS") %>% -->
<!--   gather(`OLS`, `WLS`, `MinT`,  key = Method, value = MSE) %>% -->
<!--   mutate(Method = factor(Method, levels = c("OLS", "MinT", "WLS"))) %>% -->
<!--   ggplot(aes(x = Method, y = MSE)) + -->
<!--   geom_boxplot() + facet_wrap(~ Fc_horizon) + -->
<!--   ylab("MSE") + xlab("Reconciliation Method") -->

<!-- library(scales) -->

<!-- asinh_trans <- function(){ -->
<!--   trans_new(name = 'asinh', transform = function(x) asinh(x),  -->
<!--             inverse = function(x) sinh(x)) -->
<!-- } -->

<!-- OvernightTrips_OriginalScale_MSE %>% -->
<!--   filter(`R.method`%in% c("Base", "OLS", "MinT(Shrink)", "WLS")) %>% -->
<!--   spread(key = `R.method`, value = MSE) %>% -->
<!--   mutate("Base-OLS" = Base - OLS, -->
<!--          "Base-MinT" = Base - `MinT(Shrink)`, -->
<!--          "Base-WLS" = Base - WLS) %>% -->
<!--   dplyr::select(Fc_horizon, Replication, `Base-OLS`, `Base-MinT`, `Base-WLS`) %>% -->
<!--   rename("OLS" = "Base-OLS", "MinT" = "Base-MinT", "WLS" = "Base-WLS") %>% -->
<!--   gather(`OLS`, `WLS`, `MinT`,  key = Method, value = MSE) %>% -->
<!--   mutate(Method = factor(Method, levels = c("OLS", "MinT", "WLS"))) %>% -->
<!--   ggplot(aes(x = Method, y = MSE)) + -->
<!--   geom_boxplot() + scale_y_continuous(trans = 'asinh',breaks=c(-10000,-1000,-100,0,100,1000,10000))+ -->
<!--   facet_wrap(~ Fc_horizon)+ -->
<!--   theme_bw() -->

<!-- ``` -->

<!-- # Box and whisker plots for orthogonal and oblique projections from misspecified models -->

<!-- ```{r, echo=FALSE} -->
<!-- OvernightTrips_OriginalScaleMisspecified_Fc <- read.csv("OvernightTrips_OriginalScaleMisspecified_Fc.csv")[,-1] -->

<!-- OvernightTrips_OriginalScaleMisspecified_Fc %>% -->
<!--   mutate(SquaredE = (Overnight_Trips - Overnight_Trips_Fc)^2, -->
<!--          Fc_horizon = recode(Fc_horizon, "1" = "h=1", "2" = "h=2", -->
<!--                              "3" = "h=3", "4" = "h=4", "5" = "h=5", "6" = "h=6")) %>% -->
<!--   group_by(`R.method`, Fc_horizon, Replication) %>% -->
<!--   summarise(MSE = mean(SquaredE)) -> OvernightTrips_OriginalScaleMisspecified_MSE -->

<!-- OvernightTrips_OriginalScaleMisspecified_MSE %>% -->
<!--   filter(`R.method`%in% c("Base", "OLS", "MinT(Shrink)", "WLS")) %>% -->
<!--   spread(key = `R.method`, value = MSE) %>% -->
<!--   mutate("Base-OLS" = Base - OLS, -->
<!--          "Base-MinT" = Base - `MinT(Shrink)`, -->
<!--          "Base-WLS" = Base - WLS) %>% -->
<!--   dplyr::select(Fc_horizon, Replication, `Base-OLS`, `Base-MinT`, `Base-WLS`) %>% -->
<!--   rename("OLS" = "Base-OLS", "MinT" = "Base-MinT", "WLS" = "Base-WLS") %>% -->
<!--   gather(`OLS`, `WLS`, `MinT`,  key = Method, value = MSE) %>% -->
<!--   mutate(Method = factor(Method, levels = c("OLS", "MinT", "WLS"))) %>% -->
<!--   ggplot(aes(x = Method, y = MSE)) + -->
<!--   geom_boxplot() + facet_wrap(~ Fc_horizon) + -->
<!--   ylab("MSE") + xlab("Reconciliation Method") -->

<!-- ``` -->

@@

# ME
DF_LogTrans_WL100 %>% 
  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
  summarise(ME = round(sum(ME)/1e3, digits = 2)) %>% 
  filter(Forecast_Horizon == 1) %>% 
  ungroup() %>% 
  dplyr::select(-Forecast_Horizon)-> Avg_Log_WL100_ME_h1

Avg_Log_WL100_ME_h1 %>% 
  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", 
                           Unbiased_M2 = "Unbiased (Method 2)")) %>% 
  spread(key = F.method, value = ME) %>% 
  kable(format = "latex",)

@@

Avg_Log_WL100_MSE_h1 %>% 
  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", 
                           Unbiased_M2 = "Unbiased (Method 2)")) %>% 
  spread(key = F.method, value = MSE) %>% 
  kable(format = "latex")

@@

# Log Transformation with 180 observations of training window (ME and MSE calculated over 60 replications)

```{r, echo=FALSE}
DF_LogTrans_WL180 <- read.csv("DF_LogTrans_WL180.csv")[,-1]

DF_LogTrans_WL180 <- DF_LogTrans_WL180 %>% 
  mutate(F.method=recode(F.method, `Bias` = 'Biased')) 
# so that we don't confuse Biased forecasts with ME

DF_LogTrans_WL180 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_LogTrans_WL180
DF_LogTrans_WL180 %>% mutate(ME = `Actual` - `Forecasts`) -> DF_LogTrans_WL180

# ME
DF_LogTrans_WL180 %>% 
  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
  summarise(ME = round(sum(ME)/1e3, digits = 2)) %>% 
  filter(Forecast_Horizon == 1) %>% 
  ungroup() %>% 
  dplyr::select(-Forecast_Horizon)-> Avg_Log_WL180_ME_h1

Avg_Log_WL180_ME_h1 %>% 
  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", 
                           Unbiased_M2 = "Unbiased (Method 2)")) %>% 
  spread(key = F.method, value = ME) %>% 
  kable(format = "latex",)

#MSE
DF_LogTrans_WL180 %>% 
  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
  summarise(MSE = round(mean(SquaredE)/1e3, digits = 2)) %>% 
  filter(Forecast_Horizon == 1) %>% 
  ungroup() %>% 
  dplyr::select(-Forecast_Horizon)-> Avg_Log_WL180_MSE_h1

Avg_Log_WL180_MSE_h1 %>% 
  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", 
                           Unbiased_M2 = "Unbiased (Method 2)")) %>% 
  spread(key = F.method, value = MSE) %>% 
  kable(format = "latex")

<!-- # BoxCox Transformation for $\lambda \in (0,1)$ -->

<!-- ```{r, echo=FALSE} -->
<!-- DF_BoxCoxTrans_set1 <- read.csv("OvernightTrips_BoxCoxTrans_set1_Fc.csv")[,-1] -->

<!-- DF_BoxCoxTrans_set1 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_BoxCoxTrans_set1 -->

<!-- DF_BoxCoxTrans_set1 %>% -->
<!--   group_by(`F.method`, `R.method`, Forecast_Horizon) %>% -->
<!--   summarise(MSE = round(mean(SquaredE)/1e3, digits = 2)) %>% -->
<!--   filter(Forecast_Horizon == 1) %>% -->
<!--   ungroup() %>% -->
<!--   dplyr::select(-Forecast_Horizon)-> Avg_BoxCox_set1_MSE_h1 -->

<!-- Avg_BoxCox_set1_MSE_h1 %>% -->
<!--   mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", -->
<!--                            Unbiased_M2 = "Unbiased (Method 2)")) %>% -->
<!--   spread(key = F.method, value = MSE) %>% -->
<!--   kable(format = "latex") -->

<!-- ``` -->

@@

# ME
DF_BoxCoxTrans_WL100 %>% 
  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
  summarise(ME = round(sum(ME)/1e3, digits = 2)) %>% 
  filter(Forecast_Horizon == 1) %>% 
  ungroup() %>% 
  dplyr::select(-Forecast_Horizon)-> Avg_Log_WL100_ME_h1

Avg_Log_WL100_ME_h1 %>% 
  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", 
                           Unbiased_M2 = "Unbiased (Method 2)")) %>% 
  spread(key = F.method, value = ME) %>% 
  kable(format = "latex",)

#MSE
DF_BoxCoxTrans_WL100 %>% 
  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
  summarise(MSE = round(mean(SquaredE)/1e3, digits = 2)) %>% 
  filter(Forecast_Horizon == 1) %>% 
  ungroup() %>% 
  dplyr::select(-Forecast_Horizon)-> Avg_Log_WL100_MSE_h1

Avg_Log_WL100_MSE_h1 %>% 
  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", 
                           Unbiased_M2 = "Unbiased (Method 2)")) %>% 
  spread(key = F.method, value = MSE) %>% 
  kable(format = "latex")

@@

# BoxCox Transformation for $\lambda \in (-0.5,2)$ with 180 observations of training window (ME and MSE calculated over 60 replications)

```{r, echo=FALSE}
DF_BoxCoxTrans_WL180 <- read.csv("DF_BoxCoxTrans_WL180.csv")[,-1]

DF_BoxCoxTrans_WL180 <- DF_BoxCoxTrans_WL180 %>% 
  mutate(F.method=recode(F.method, `Bias` = 'Biased')) 
# so that we don't confuse Biased forecasts with ME

DF_BoxCoxTrans_WL180 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_BoxCoxTrans_WL180
DF_BoxCoxTrans_WL180 %>% mutate(ME = `Actual` - `Forecasts`) -> DF_BoxCoxTrans_WL180

# ME
DF_BoxCoxTrans_WL180 %>% 
  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
  summarise(ME = round(sum(ME)/1e3, digits = 2)) %>% 
  filter(Forecast_Horizon == 1) %>% 
  ungroup() %>% 
  dplyr::select(-Forecast_Horizon)-> Avg_Log_WL100_ME_h1

Avg_Log_WL100_ME_h1 %>% 
  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", 
                           Unbiased_M2 = "Unbiased (Method 2)")) %>% 
  spread(key = F.method, value = ME) %>% 
  kable(format = "latex",)

#MSE
DF_BoxCoxTrans_WL180 %>% 
  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
  summarise(MSE = round(mean(SquaredE)/1e3, digits = 2)) %>% 
  filter(Forecast_Horizon == 1) %>% 
  ungroup() %>% 
  dplyr::select(-Forecast_Horizon)-> Avg_Log_WL100_MSE_h1

Avg_Log_WL100_MSE_h1 %>% 
  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", 
                           Unbiased_M2 = "Unbiased (Method 2)")) %>% 
  spread(key = F.method, value = MSE) %>% 
  kable(format = "latex")

>>>>

library(tidyverse)
library(Matrix)
library(hts)
library(readr)
library(tibble)
library(kableExtra)
library(tsutils)
# library(reshape2)
```

@@

# ME
DF_LogTrans_WL100 %>%  
  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
  summarise(ME = round(sum(ME)/1e3, digits = 2)) %>% 
  filter(Forecast_Horizon == 1) %>% 
  ungroup() %>% 
  dplyr::select(-Forecast_Horizon) -> Avg_Log_WL100_ME_h1

# Make everything percentage improvement
Avg_Log_WL100_ME_h1 <- Avg_Log_WL100_ME_h1 %>% 
  mutate(ME=ME/Avg_Log_WL100_ME_h1[1,]$ME)

Avg_Log_WL100_ME_h1 %>% 
  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", 
                           Unbiased_M2 = "Unbiased (Method 2)")) %>% 
  spread(key = F.method, value = ME) %>% 
  kable(format = "latex",digits = 2)

@@

# Make everything percentage improvement
Avg_Log_WL100_MSE_h1 <- Avg_Log_WL100_MSE_h1 %>% 
  mutate(MSE=MSE/Avg_Log_WL100_MSE_h1[1,]$MSE)

Avg_Log_WL100_MSE_h1 %>% 
  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", 
                           Unbiased_M2 = "Unbiased (Method 2)")) %>% 
  spread(key = F.method, value = MSE) %>% 
  kable(format = "latex", digits = 2)

@@

@@

# ME
DF_BoxCoxTrans_WL100 %>% 
  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
  summarise(ME = round(sum(ME)/1e3, digits = 2)) %>% 
  filter(Forecast_Horizon == 1) %>% 
  ungroup() %>% 
  dplyr::select(-Forecast_Horizon)-> Avg_BoxCox_WL100_ME_h1

# Make everything percentage improvement
Avg_BoxCox_WL100_ME_h1 <- Avg_BoxCox_WL100_ME_h1 %>% 
  mutate(ME=ME/Avg_BoxCox_WL100_ME_h1[1,]$ME)

Avg_BoxCox_WL100_ME_h1 %>% 
  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", 
                           Unbiased_M2 = "Unbiased (Method 2)")) %>% 
  spread(key = F.method, value = ME) %>% 
  kable(format = "latex",digits = 2)

#MSE
DF_BoxCoxTrans_WL100 %>% 
  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
  summarise(MSE = round(mean(SquaredE)/1e3, digits = 2)) %>% 
  filter(Forecast_Horizon == 1) %>% 
  ungroup() %>% 
  dplyr::select(-Forecast_Horizon)-> Avg_BoxCox_WL100_MSE_h1

Avg_BoxCox_WL100_MSE_h1 <- Avg_BoxCox_WL100_MSE_h1 %>%
  mutate(MSE=MSE/Avg_BoxCox_WL100_MSE_h1[1,]$MSE)

Avg_BoxCox_WL100_MSE_h1 %>% 
  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", 
                           Unbiased_M2 = "Unbiased (Method 2)")) %>% 
  spread(key = F.method, value = MSE) %>% 
  kable(format = "latex", digits = 2)

@@

### 2020-01-21 Application-R/Application-TourismData/Final-results/TourismData-Final-resultsR1.tex
Calculating Nemenyi tests

\begin{tabular}{l|r|r|r}
\hline
R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\
\hline
Base & 99.98 & 52.70 & 140.46\\
\hline
Bottom-up & 176.31 & 64.42 & 271.73\\
\hline
MinT(Shrink) & 74.31 & 50.50 & 109.89\\
\hline
OLS & 50.73 & 38.64 & 65.82\\
\hline
WLS & 121.11 & 57.50 & 174.35\\
\hline
\end{tabular}

\begin{tabular}{l|r|r|r}
\hline
R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\
\hline
Base & 4.47 & 4.43 & 4.51\\
\hline
Bottom-up & 6.36 & 5.26 & 8.06\\
\hline
MinT(Shrink) & 4.32 & 4.16 & 4.61\\
\hline
OLS & 4.34 & 4.31 & 4.36\\
\hline
WLS & 4.82 & 4.38 & 5.43\\
\hline
\end{tabular}

\hypertarget{log-transformation-with-180-observations-of-training-window-me-and-mse-calculated-over-60-replications}{%
\section{Log Transformation with 180 observations of training window (ME
and MSE calculated over 60
replications)}\label{log-transformation-with-180-observations-of-training-window-me-and-mse-calculated-over-60-replications}}

\begin{tabular}{l|r|r|r}
\hline
R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\
\hline
Base & 90.45 & 67.34 & 109.95\\
\hline
Bottom-up & 152.69 & 98.06 & 197.11\\
\hline
MinT(Shrink) & 64.64 & 59.36 & 85.54\\
\hline
OLS & 41.62 & 35.92 & 47.51\\
\hline
WLS & 110.65 & 79.64 & 136.58\\
\hline
\end{tabular}

\begin{tabular}{l|r|r|r}
\hline
R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\
\hline
Base & 4.89 & 4.78 & 5.08\\
\hline
Bottom-up & 9.71 & 6.97 & 12.70\\
\hline
MinT(Shrink) & 4.75 & 4.63 & 5.35\\
\hline
OLS & 4.67 & 4.60 & 4.81\\
\hline
WLS & 6.33 & 5.22 & 7.58\\
\hline
\end{tabular}

@@

\begin{tabular}{l|r|r|r}
\hline
R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\
\hline
Base & 94.38 & 59.71 & 129.50\\
\hline
Bottom-up & 163.07 & 71.22 & 242.39\\
\hline
MinT(Shrink) & 71.10 & 57.94 & 96.92\\
\hline
OLS & 50.70 & 43.13 & 70.16\\
\hline
WLS & 113.67 & 65.49 & 157.17\\
\hline
\end{tabular}

\begin{tabular}{l|r|r|r}
\hline
R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\
\hline
Base & 4.59 & 4.52 & 4.78\\
\hline
Bottom-up & 6.21 & 5.31 & 7.46\\
\hline
MinT(Shrink) & 4.29 & 4.17 & 4.54\\
\hline
OLS & 4.46 & 4.40 & 4.63\\
\hline
WLS & 4.77 & 4.42 & 5.23\\
\hline
\end{tabular}

\hypertarget{boxcox-transformation-for-lambda-in--0.52-with-180-observations-of-training-window-me-and-mse-calculated-over-60-replications}{%
\section{\texorpdfstring{BoxCox Transformation for
\(\lambda \in (-0.5,2)\) with 180 observations of training window (ME
and MSE calculated over 60
replications)}{BoxCox Transformation for \textbackslash lambda \textbackslash in (-0.5,2) with 180 observations of training window (ME and MSE calculated over 60 replications)}}\label{boxcox-transformation-for-lambda-in--0.52-with-180-observations-of-training-window-me-and-mse-calculated-over-60-replications}}

\begin{tabular}{l|r|r|r}
\hline
R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\
\hline
Base & 88.91 & 73.25 & 103.24\\
\hline
Bottom-up & 142.37 & 98.60 & 178.09\\
\hline
MinT(Shrink) & 63.30 & 62.84 & 75.61\\
\hline
OLS & 47.03 & 44.71 & 51.25\\
\hline
WLS & 105.78 & 83.93 & 124.99\\
\hline
\end{tabular}

\begin{tabular}{l|r|r|r}
\hline
R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\
\hline
Base & 4.61 & 4.58 & 4.72\\
\hline
Bottom-up & 9.17 & 7.00 & 11.43\\
\hline
MinT(Shrink) & 4.50 & 4.53 & 4.82\\
\hline
OLS & 4.43 & 4.43 & 4.52\\
\hline
WLS & 6.24 & 5.45 & 7.11\\
\hline
\end{tabular}

>>>>

\begin{tabular}{l|r|r|r}
\hline
R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\
\hline
Base & 1.00 & 0.53 & 1.40\\
\hline
Bottom-up & 1.76 & 0.64 & 2.72\\
\hline
MinT(Shrink) & 0.74 & 0.51 & 1.10\\
\hline
OLS & 0.51 & 0.39 & 0.66\\
\hline
WLS & 1.21 & 0.58 & 1.74\\
\hline
\end{tabular}

\begin{tabular}{l|r|r|r}
\hline
R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\
\hline
Base & 1.00 & 0.99 & 1.01\\
\hline
Bottom-up & 1.42 & 1.18 & 1.80\\
\hline
MinT(Shrink) & 0.97 & 0.93 & 1.03\\
\hline
OLS & 0.97 & 0.96 & 0.98\\
\hline
WLS & 1.08 & 0.98 & 1.21\\
\hline
\end{tabular}

@@

\begin{tabular}{l|r|r|r}
\hline
R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\
\hline
Base & 1.00 & 0.63 & 1.37\\
\hline
Bottom-up & 1.73 & 0.75 & 2.57\\
\hline
MinT(Shrink) & 0.75 & 0.61 & 1.03\\
\hline
OLS & 0.54 & 0.46 & 0.74\\
\hline
WLS & 1.20 & 0.69 & 1.67\\
\hline
\end{tabular}

\begin{tabular}{l|r|r|r}
\hline
R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\
\hline
Base & 1.00 & 0.98 & 1.04\\
\hline
Bottom-up & 1.35 & 1.16 & 1.63\\
\hline
MinT(Shrink) & 0.93 & 0.91 & 0.99\\
\hline
OLS & 0.97 & 0.96 & 1.01\\
\hline
WLS & 1.04 & 0.96 & 1.14\\
\hline
\end{tabular}
